RDT - Gold Standard Equivalence

### 2023-02-24 notebooks/R/RDT-equivalence.rmd
Set up DrWatson Julia project and Quarto project, and move R code to subdirs

```{r}
stoch_test3 %>%
  ggplot() +
  geom_contour_filled(aes(x = sens, y = spec, z = min_test_dis_pos_diff)) +
  scale_fill_manual(values = met.brewer("Robert", 11)) +
  labs(
    title = "Minimum Difference in Test Positives and Disease Positives",
    subtitle = glue("Prevalence = {prev}, Total Tests = {tot}")
  )
```

```{r}
stoch_test3 %>%
  ggplot() +
  geom_contour_filled(aes(x = sens, y = spec, z = quantile_10)) +
  scale_fill_manual(values = met.brewer("Robert", 11)) +
  labs(
    title = "10% Quantile Difference in Test Positives and Disease Positives",
    subtitle = glue("Prevalence = {prev}, Total Tests = {tot}")
  )
```

>>>>

```{r}
stoch_test3 %>%
  ggplot() +
  geom_contour_filled(aes(x = sens, y = spec, z = min_test_dis_pos_diff)) +
  scale_fill_manual(values = met.brewer("Nattier", 11)) +
  labs(
    title = "Minimum Difference in Test Positives and Disease Positives",
    subtitle = glue("Prevalence = {prev}, Total Tests = {tot}")
  )
```

```{r}
stoch_test3 %>%
  ggplot() +
  geom_contour_filled(aes(x = sens, y = spec, z = quantile_10)) +
  scale_fill_manual(values = met.brewer("Nattier", 11)) +
  labs(
    title = "10% Quantile Difference in Test Positives and Disease Positives",
    subtitle = glue("Prevalence = {prev}, Total Tests = {tot}")
  )
```
